% Document Type: LaTeX
% Master File: agreement.tex
\documentstyle[times]{article}

\begin{document}
\ \\
{\huge {\bf AGREEMENT}}
\begin{large}
\\
\begin{bf}
RESEARCH SOFTWARE\\
Distributed by the Industrial Liaison Program, Department of
Electrical Engineering and Computer Sciences / Electronics Research
Laboratory\\
University of California at Berkeley
\end{bf}

\vspace*{2ex}

\ \\
\begin{bf}
This form must be signed on the reverse side and returned to:\\
\vspace*{2ex}\\
Cindy Manly-Fields\\
Industrial Liaison Program Office\\
479 Cory Hall\\
University of California\\
Berkeley, CA    94720\\
USA
\end{bf}
\end{large}

\vspace*{3ex}

This form specifies the terms under which the software and
documentation contained in the {\bf Oct Tools Distribution} are provided.

The software is distributed as is, completely without warranty and
service support.  The University of California and its employees shall
not be liable for the condition or performance of the software.  The
software and documentation provided under this agreement are for
internal use only within your organization.  

The University does not warrant that it owns the copyright or other
proprietary rights to all software and documentation provided under
this agreement, notwithstanding any copyright notice, and shall not be
liable for any infringement of copyright or other proprietary rights
brought by third parties against the recipient of the software and
documentation provided under this agreement.

THE UNIVERSITY HEREBY DISCLAIMS ALL IMPLIED WARRANTIES, INCLUDING THE
IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR
PURPOSE.
THE UNIVERSITY SHALL NOT BE LIABLE FOR ANY DAMAGES INCURRED BY THE
RECIPIENT IN USE OF THE SOFTWARE AND DOCUMENTATION, INCLUDING DIRECT,
INDIRECT, SPECIAL, INCIDENTAL, OR CONSEQUENTIAL DAMAGES.

To facilitate the use of the programs within your organization within
the United States, unless otherwise stated, your organization may make
an unlimited number of copies of documentation and code for internal
use within your organization, provided that the copies bear the
copyright notice appearing on the documentation and code and are
clearly marked as being for internal use only.

The recipient's right to redistribute a program is subject to a
separate license agreement.  Should you wish to redistribute the code,
contact the developer of the code directly by writing to the
Industrial Liaison Program Software Distribution Coordinator.

The software and documentation provided under this agreement may be
forwarded to your organization's offices outside the United States
provided that you sign the letter of assurance, return said letter to
the Industrial Liaison Program, and comply with all applicable United
States laws and regulations regarding the export of technology.

The Industrial Liaison Program does not distribute software to
organizations or individuals outside the United States but does
distribute documentation, provided that you sign the letter of
assurance, return said letter to the Industrial Liaison Program, and
comply with all applicable United States laws and regulations
regarding the export of technology.

\vspace*{3ex}

\begin{tabular}{ll}
& \\
& \\
SIGNATURE: & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
& \\
& \\
NAME: & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
& \\
& \\
TITLE: & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
& \\
& \\
ORGANIZATION: & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
& \\
& \\
DATE: & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{tabular}

\end{document}
